\documentclass[line,margin]{res}
    \usepackage[none]{hyphenat}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \begin{document}
\name{{\LARGE Jani Anttonen}}
\address{jani.anttonen@protonmail.ch | +358 40 589 0039 | Turku, Finland | https://janianttonen.com}
\begin{resume}
	\vspace{-5mm}
	        
	
	\section{Education}
	\textbf{University of Turku}, {\sl MSc in Computer Science} \hfill Sep 2017 | Jun 2022\\Turku, Finland\\\\
	\textbf{University of Turku}, {\sl BS in Computer Science} \hfill Sep 2012 | Jun 2017\\Turku, Finland\\\\
	\textbf{Turku Vocational Institute}, {\sl Business Information Technology} \hfill 2007 | 2010\\Turku, Finland
	\section{Work Experience}
	\textbf{Equilibrium}, {\sl Software Engineer}\hfill Mar 2018 | Aug 2023\\\begin{itemize} \itemsep 3pt
	\item Software architecture, design and development in the fields of public blockchains, decentralized finance and peer to peer networking. Worked with Typescript, React, Next.js, Solidity, Python \& Go. Also involved in product \& business development. First developer at the company.
	\end{itemize}
	\textbf{Marshall AI}, {\sl Software Engineer}\hfill Jan 2018 | Aug 2019\\\begin{itemize} \itemsep 3pt
	\item Full-stack progressive web app development involving real-time video, picture and data feeds, digital twins etc. Involved with sales \& client communication using agile development methods. React, Node.js \& Python, prototyping using different machine learning methods, time series data analysis etc.
	\end{itemize}
	\textbf{Nordic Venture Family}, {\sl Software Developer}\hfill Jun 2015 | Jan 2018\\Turku, Finland\\\begin{itemize} \itemsep 3pt
	\item The venture studio behind Equilibrium \& Marshall AI. Before my tenures in Equilibrium and Marshall AI, I was a web developer mainly responsible for the websites of the various startups NVF spawned. Worked with Wordpress, GatsbyJS and good old HTML \& CSS.
	\end{itemize}
	\textbf{Telia}, {\sl Technical Customer Service Adviser}\hfill May 2014 | Sep 2014\\Turku, Finland\\\begin{itemize} \itemsep 3pt
	\item Then called TeliaSonera, I helped their customers over the phone and support emails with their internet and IPTV related technical problems in one of the largest ISPs in the country. Learned a bunch of how both wired and wireless networks work.
	\end{itemize}
	\textbf{University of Turku, Turku Teacher Training School}, {\sl IT Support / Janitor}\hfill Jul 2011 | Jun 2013\\Turku, Finland\\\begin{itemize} \itemsep 3pt
	\item All-around IT support around the school. Also worked some weeknights as a janitor during my studies.
	\end{itemize}
	\section{Skills}
	\begin{tabular}{@{}ll}
		\textbf{Lang}:    & React, Typescript, Solidity, Python, Go, Rust, Java, CSS \\
		\textbf{Tech}:    & Docker, UNIX, SQL \& NoSQL, Next.js, Foundry, Truffle    \\
		\textbf{Methods}: & Agile, Scrum, Kanban, Async \& Remote, TDD               \\
		\textbf{Cloud}:   & Vercel, Netlify, AWS, VPS, GitHub                        \\
	\end{tabular}
	
	
	\ 
\end{resume}
\end{document}